Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-07-19 manuscript.tex
Update manuscript.tex

\textcolor{red}{As the size and number of communities is strictly dependent on the \emph{k}NN graph generation, we investigated how different parameters (\emph{i.e.} number of principal components and number of neighbors) affect the partition structure (Fig. \ref{Figure_Comm_Count} and \ref{Figure_Comm_Size}). We found, as a general pattern, that increasing the number of neighbors results in more granular structure at level 0, whereas increasing the number of PCs works in opposite direction. Looking at the agreement among different partitions, we found that it is consistent among different solutions, both at level 0 and level 1, with the exception of models for graph derived with low number of PC (Fig. \ref{Figure_Clustermap_L0})}
%\subsection*{PPBM?}

@@

Identification of cells sharing similar properties in single cell experiments is of paramount importance. A large number of approaches have been described, although the standardisation of analysis pipelines converged to methods that are based on modularity optimisation. We tackled the biological problem using a different approach, nSBM, which has several advantages over existing techniques. \textcolor{red}{As  random data may have modular structure \cite{guimer_2004}, an important property of our approach is that it does not overfit data by finding partitions when, in fact, the are not.} Another important advantage is \textcolor{red}{that} the hierarchical definition of cell groups eliminates the choice of an arbitrary threshold on clustering resolution. In addition, we showed that the hierarchy itself could have a biological interpretation, implying that the hierarchical model is a valid representation of the cell ensemble.

>>>>

\textcolor{red}{As the size and number of communities is strictly dependent on the \emph{k}NN graph generation, we investigated how different parameters (\emph{i.e.} number of principal components and number of neighbors) affect the partition structure (Fig. \ref{Figure_Comm_Count} and \ref{Figure_Comm_Size}). We found, as a general pattern, that increasing the number of neighbors results in more granular structure at level 0, whereas increasing the number of PCs works in opposite direction. Looking at the agreement among different partitions, we found that it is consistent among different solutions, both at level 0 and level 1, with the exception of models for graph derived with low number of PC (Fig. \ref{Figure_Clustermap_L0}).}
%\subsection*{PPBM?}

@@

Identification of cells sharing similar properties in single cell experiments is of paramount importance. A large number of approaches have been described, although the standardisation of analysis pipelines converged to methods that are based on modularity optimisation. We tackled the biological problem using a different approach, nSBM, which has several advantages over existing techniques. \textcolor{red}{As random data may have modular structure \cite{guimer_2004}, an important property of our approach is that it does not overfit data by finding partitions when, in fact, there are not.} Another important advantage is \textcolor{red}{that} the hierarchical definition of cell groups eliminates the choice of an arbitrary threshold on clustering resolution. In addition, we showed that the hierarchy itself could have a biological interpretation, implying that the hierarchical model is a valid representation of the cell ensemble.
